Low prevalence of \emph{a priori} power analyses in motor behavior research

### 2022-07-13 docs/preprint/preprint.tex
update: fix behaviour spelling in github links

\noindent The preregistration, data, and scripts can be accessed using either of the following links: \url{https://osf.io/wsdpv/} or \url{https://github.com/cartermaclab/proj_power-motor-behavior}.

>>>>

\noindent The preregistration, data, and scripts can be accessed using either of the following links: \url{https://osf.io/wsdpv/} or \url{https://github.com/cartermaclab/proj_power-motor-behaviour}.
